### 2021-04-22 yfcc100m/paper/vldb2021/reviewer_response.txt

Reviews: Point addressed
========================================
Reviewer #1

Reviewer #4

Reviewer #5
    D4: Fixed all typos

### 2021-04-22 yfcc100m/paper/vldb2021/eval.tex
added file for reviewer responses and fixed typos from reviewer 5

Given that there are no other open-source systems that provide similar
functionality and interfaces as VDMS (i.e., transactionally dealing with images
and metadata behind a single interface), we have implemented two equivalent
visual data management system as baselines,
desing specifically for the image search use case,
and comprised of a combination of widely available, off-the-shelf components.
The first baseline uses MySQL Server 5.7 (for storing metadata),
Apache Web Server 2.4.18 (as interface for image access), and
OpenCV 3.3 (to provide pre-processing operations on images).
We chose Apache Web Server to work as a file server (serving the image files),
because it provides the lowest possible overhead
(when compared to other object store system), at the expenses of providing less
functionality (authentication, data integrity checking, etc).
The other baseline system replaces the MySQL Server 5.7 with a
most advanced open-source relational database, PostgreSQL 9.5 \cite{postgresql}.
We decided to use relational databases in the baseline systems instead of
non-relational databases because of their maturity, and also because it is
the most common tools used for storing and querying metadata
~\cite{Jatana2012, li_2019}:

@@

\textbf{PostgreSQL-Based System (\textit{postgresql}):}
Each PostgreSQL database is created in the exact same manner as MySQL
where data is represented as three tables:
\textit{images}, \textit{taglist}, and \textit{taglist}.
PostgreSQL works well out-of-box and optimizations were not necessary,
as in MySQL, to load or execute queries.
When executing queries for larger databases,
it is pertinent to have enough disk space for both
the database and tablespace.
The tablespace is associated with a database and stores the temporary files
created within the database object ~\cite{postgresql}.
When processing the larger databases, additional
storage may be needed for the tablespace or a diskfull error may occur.
To avoid this, we allocated a separate SSD disk specifically
for the tablespace of all databases.
This was required, specially for 100M database, in order to make the queries
complete execution without failures, and represented a big disadvantage
in terms of the disk space footprint during query execution.

@@

\begin{figure}[ht]
% WAS: begin{figure*}[ht]; textwidth
\includegraphics[width=\columnwidth]{figures/plot_conc_dbsize_10M_mosaic_results_throughput}
\caption{Concurrency Analysis for all the queries using the 10M database).
Each figure shows the throughput (images per second) when retrieving
resized versions of the images as the number of concurrent clients increases.
Hardware concurrency (number of physical cores in each system)
is 56.}
\label{fig:concurrency_comparison_10M}
\end{figure}

>>>>

Given that there are no other open-source systems that provide similar
functionality and interfaces as VDMS (i.e., transactionally dealing with images
and metadata behind a single interface), we have implemented two equivalent
visual data management system as baselines,
design specifically for the image search use case,
and comprised of a combination of widely available, off-the-shelf components.
The first baseline uses MySQL Server 5.7 (for storing metadata),
Apache Web Server 2.4.18 (as interface for image access), and
OpenCV 3.3 (to provide pre-processing operations on images).
We chose Apache Web Server to work as a file server (serving the image files),
because it provides the lowest possible overhead
(when compared to other object store system), at the expenses of providing less
functionality (authentication, data integrity checking, etc).
The other baseline system replaces the MySQL Server 5.7 with a
most advanced open-source relational database, PostgreSQL 9.5 \cite{postgresql}.
We decided to use relational databases in the baseline systems instead of
non-relational databases because of their maturity, and also because it is
the most common tools used for storing and querying metadata
~\cite{Jatana2012, li_2019}:

@@

\textbf{PostgreSQL-Based System (\textit{postgresql}):}
Each PostgreSQL database is created in the exact same manner as MySQL
where data is represented as three tables:
\textit{images}, \textit{taglist}, and \textit{autotags}.
PostgreSQL works well out-of-box and optimizations were not necessary,
as in MySQL, to load or execute queries.
When executing queries for larger databases,
it is pertinent to have enough disk space for both
the database and tablespace.
The tablespace is associated with a database and stores the temporary files
created within the database object ~\cite{postgresql}.
When processing the larger databases, additional
storage may be needed for the tablespace or a diskfull error may occur.
To avoid this, we allocated a separate SSD disk specifically
for the tablespace of all databases.
This was required, specially for 100M database, in order to make the queries
complete execution without failures, and represented a big disadvantage
in terms of the disk space footprint during query execution.

@@

\begin{figure}[ht]
% WAS: begin{figure*}[ht]; textwidth
\includegraphics[width=\columnwidth]{figures/plot_conc_dbsize_10M_mosaic_results_throughput}
\caption{Concurrency Analysis for all the queries using the 10M database.
Each figure shows the throughput (images per second) when retrieving
resized versions of the images as the number of concurrent clients increases.
Hardware concurrency (number of physical cores in each system)
is 56.}
\label{fig:concurrency_comparison_10M}
\end{figure}

### 2021-04-22 yfcc100m/paper/vldb2021/intro.tex
minor edits to intro
minor edit to intro
added file for reviewer responses and fixed typos from reviewer 5

To illustrate the point on the need for multiple system to build the data
infrastructure for applications,
consider a ML developer constructing a pipeline for extracting
brain tumor information from existing brain images in a classic medical
imaging use case.
This requires assigning consistent identifiers for the scans and adding their
\textit{metadata} in a relational or key-value database\cite{kumar2017data}.
If the queries require a search over patient information,
then patients are associated with their brain scans.
If the queries require a search over patient information,
then patients are associated with their brain scans.
Finally, if the ML pipeline needs images with a different resolution
than the original, there is additional compute
diverted towards pre-processing the original images.
All these steps require understanding different software
solutions that provide various functionalities that can then be stitched
together with many scripts for this specific use case.
Moreover, if the pipeline identifies new metadata to be added for
the tumor images, most databases make it hard to change the schema on the fly.
As another example, many applications can be studied through the use of large
and publicly available datasets.
Applications include basic image search functionality (through the use
of human-generated tags), advanced image search through the use of
machine-generated tags and feature vectors\cite{imagesearch, qin2020similarity}
for each image, and video summarization.
For these use-cases, the usual first step consists on selecting a
subset of the data before running any processing, and a large effort
is devoted to filtering, curating, and pre-processing the data.
Selecting subsets of data is by itself a time consuming task,
as it involves loading all metadata into a solution that enables searching
based on tags (relational database, graph database, csv files, etc), and
building the necessary pipelines for querying and retrieving the right data.

>>>>

To illustrate the point on the need for multiple systems to build the data
infrastructure for applications,
consider a ML developer constructing a pipeline for extracting
brain tumor information from existing brain images in a classic medical
imaging use case.
This requires assigning consistent identifiers for the scans and adding their
\textit{metadata} in a relational or key-value database\cite{kumar2017data}.
If the queries require a search over patient information,
then patients are associated with their brain scans.
Finally, if the ML pipeline needs images with a different resolution
than the original, there is additional compute
diverted towards pre-processing the original images.
All these steps require understanding different software
solutions that provide various functionalities that can then be stitched
together with many scripts for this specific use case.
Moreover, if the pipeline identifies new metadata to be added for
the tumor images, most databases make it hard to change the schema on the fly.
As another example, many applications can be studied through the use of large
and publicly available datasets.
Applications include basic image search functionality (through the use
of human-generated tags), advanced image search through the use of
machine-generated tags and feature vectors\cite{imagesearch, qin2020similarity}
for each image, and video summarization.
For these use-cases, the usual first step consists on selecting a
subset of the data before running any processing, and a large effort
is devoted to filtering, curating, and pre-processing the data.
Selecting subsets of data is by itself a time consuming task,
as it involves loading all metadata into a solution that enables searching
based on tags (relational database, graph database, csv files, etc), and
building the necessary pipelines for querying and retrieving the right data.
